NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-01-04 Manuscript/manuscriptPS.tex
Update table containing simulated systems by adding links to the simulation data delivered by Tom Piggot

@@

    DOPS/Na$^+$  & CHARMM36 \cite{??}  \todoi{Correct citation for CHARMM DOPS}      &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{By Piggot: http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1491425687561\#c4932902612512697301. We need to decide the switching version or discuss this somehow.}  \\
    DOPS/Na$^+$  & CHARMM36ua \cite{??} \todoi{Correct citation for CHARMMua DOPS}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the switching version or discuss this somehow. Data to be uploaded in Zenodo?}  \\
    DOPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the cut-off version or discuss this somehow. Data to be uploaded in Zenodo?}  \\

@@

    DOPS/Na$^+$  & Berger \cite{mukhopadhyay04}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. Data to be uploaded in Zenodo?}  \\
    DOPS/Na$^+$  & GROMOS-CKP \cite{??} \todoi{Correct citation(s) for CKP.}       &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide between RF and PME or discuss this somehow. Data to be uploaded in Zenodo?}  \\

@@

    POPS/Na$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPS}        &0 & 0        & 128 			   		& 4480 & 0  & 298  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the switching version or discuss this somehow. Data to be uploaded in Zenodo?}  \\
    POPS/Na$^+$  & CHARMM36ua \cite{??} \todoi{Correct citation for CHARMMua DOPS}        &0 & 0        & 128 			   		& 4480 & 0  & 298  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the switching version or discuss this somehow. Data to be uploaded in Zenodo?}  \\
    POPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 128 			   		& 4480 & 0  & 298  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the cut-off version or discuss this somehow. Data to be uploaded in Zenodo?}  \\

@@

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for the computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{Check and report all the counterions. There may be some simulation data 
    sets with both Na+ and K+ ions?}
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
  Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}. Here ÒMÓ indicates a magnitude problem, ÒFÓ a forking problem; letter size increases with problem severity. Color scheme: Òwithin experimental errorÓ (dark green), Òalmost within experimental errorÓ (light green), Òclear deviation from experimentsÓ (light red), and Òmajor deviation from experimentsÓ (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
  \todo{CHARMM36-UA point for alpha in wrong place?}
\end{figure}

>>>>

   CKP1 referes to the version with Berger/chiu NH3 charges compatible with Berger
   and CKP2 to the version with more Gromos compatible version.

@@

    DOPS/Na$^+$  & CHARMM36 \cite{??}  \todoi{Correct citation for CHARMM DOPS}      &0 & 0 & 128 & 4480 & 0  & 303  & 500 & 100 & \cite{charmm36DOPS303K} \\
    DOPS/Na$^+$  & CHARMM36ua \cite{??} \todoi{Correct citation for CHARMMua DOPS}        &0 & 0        & 128 & 4480 & 0  & 303  & 500 & 100 & \cite{charmm36uaDOPS303K} \\
    DOPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 128 	& 4480  & 0  & 303  & 500 & 100 & \cite{slipidsDOPS303K} \\

@@

    DOPS/Na$^+$  & Berger \cite{mukhopadhyay04}    &0 & 0        & 128  & 4480  & 0  & 303  & 500 & 100 & \cite{bergerDOPS303K} \\
    DOPS/Na$^+$  & GROMOS-CKP1 \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 303  & 500 & 100 & \cite{ckp1DOPS303K} \\
    DOPS/Na$^+$  & GROMOS-CKP2 \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 303  & 500 & 100 & \cite{ckp2DOPS303K} \\

@@

    POPS/Na$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPS}&0 & 0 & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{charmm36POPS298K} \\
    POPS/Na$^+$  & CHARMM36ua \cite{??} \todoi{Correct citation for CHARMMua DOPS}  &0 & 0 & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{charmm36uaPOPS298K} \\
    POPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{slipidsPOPS298K} \\
    POPS/Na$^+$  & Berger \cite{??}        &0 & 0        & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{bergerPOPS298K} \\
    POPS/Na$^+$  & MacRog \cite{maciejewski14}  &0 & 0        & 128 & 5120 & 0  & 298  & 200 & ? \todoi{Equilibration?} & \cite{macrogPOPS298K} \\
    POPS/Na$^+$  & GROMOS-CKP1 \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp1POPS303K} \\
    POPS/Na$^+$  & GROMOS-CKP2 \cite{??} \todoi{Correct citation(s) for CKP.} &0 & 0  & 128 & 4480 & 0  & 298  & 500 & 100 & \cite{ckp2POPS303K} \\

@@

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for the computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{Check and report all the counterions. There may be some simulation data 
    sets with both Na+ and K+ ions?}
  \todo{CHARMM36-UA point for alpha in wrong place?}
  \todo{MacRog POPS data missing. The equilibration yet to be checked, thought.}
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with 
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?}
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
  Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}. Here ÒMÓ indicates a magnitude problem, ÒFÓ a forking problem; letter size increases with problem severity. Color scheme: Òwithin experimental errorÓ (dark green), Òalmost within experimental errorÓ (light green), Òclear deviation from experimentsÓ (light red), and Òmajor deviation from experimentsÓ (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
\end{figure}
